Mendelian randomization for causal inference in Genome-wide association studies

### 2022-01-27 mr-review.Rmd
added a citation
started materials on OMR

Mendelian randomization with one instrument uses a single genetic marker 
as the proxy ("instrument" or "instrumental variable") for the "exposure", or 
putative cause, in a causal inference study. When the genetic marker is a single
nucleotide polymorphism on an autosome, the cohort is partitioned into three 
classes, two homozygotes and a heterozygote, based on genotypes for that marker.

@@

@@

@@

@@

>>>>

Mendelian randomization with one instrument uses a single genetic marker 
as the proxy ("instrument" or "instrumental variable") for the "exposure" in a causal inference study. When the genetic marker is a single
nucleotide polymorphism on an autosome, the cohort is partitioned into three 
classes, two homozygotes and a heterozygote, based on genotypes for that marker.

@@

The first, often termed the

@@

@yuan_testing_2020

@@

## Omnigenic MR

Recent research on the omnigenic hypothesis, which posits 
that every SNP's effect on a trait is nonzero, has informed
MR methods development [@Boyle2017]. @wang_mendelian_nodate 
recognized the limitations of previous MR methods in the 
context of the omnigenic hypothesis. To accommodate the possibility
that a trait is influenced by many genome-wide small effects,

@@

# References
